Speed and strength of epidemic intervention

### 2019-07-19 doc/speedstrength.tex
Trying to build the pretty part of the narrative

Imagine a control measure that proportionally reduces $K$, so that the post-intervention kernel $\hat K = K/\theta$.  The factorization \eqref{speed} show that the reduction needed to prevent invasion (or to eliminate disease)  is exactly \RR. We call $\theta$ the ``strength'' of the intervention; transmission is interrupted when the strength of the intervention is larger than the strength of spread.

@@

We define the strength of the intervention $L$ to be $\theta = \RR/\Rhat$. It is then straightforward to show that $\theta$ is the harmonic mean of $L(\tau)$ weighted by generation-interval distribution.

\begin{equation}
	\theta = 1/\langle 1/L(\tau) \rangle_{g(\tau)},
\end{equation}

@@

Like $g$, $b$ is a distribution: in this case the initial backward generation interval, which gives the distribution of realized generation times when the disease spreads exponentially.

Infection kernel, $K(\tau)$, describes the rate at which secondary infections are 
expected to be caused by an infected individual, on \emph{average} (see Park 2019
for distinction between individual- and population-level infection kernel). Infection
kernel can be decomposed into two parts: reproduction number, 
$$
\Ro = \int K(s) ds,
$$ 
and the generation-interval distribution, 
$$
$$
which represents the expected time distribution of the secondary cases. The 
generation-interval distribution plays an important role in linking speed and
strength of an epidemic.

	Define intervention speed ($\phi = r - \hat r$):
	$$
	1 = \left\langle \frac{\exp(\phi \tau) }{L(\tau)} \right\rangle_{b(\tau)}
	$$
	sort of a mean associated with $L(\tau)$; outbreak controlled if $\phi > r$ (not affected by $r$).

>>>>

Imagine a control measure that proportionally reduces $K$, for example by protecting a fixed fraction of susceptibles. We then have:
\begin{equation}
	\hat K(\tau) = (\RR/\theta) g(\tau).
\end{equation}
Since $g$ is a distribution, the reduction needed to prevent invasion (or to eliminate disease)  is exactly $\theta=\RR$. We call $\theta$ the ``strength'' of the intervention; transmission is interrupted when the strength of the intervention is larger than the strength of spread.

@@

We define the strength of the intervention $L$ to be $\theta = \RR/\Rhat$. It is then straightforward to show that $\theta$ is the harmonic mean of $L(\tau)$ weighted by generation-interval distribution:
\begin{equation}
	\theta = 1/\langle 1/L(\tau) \rangle_{g(\tau)}.
\end{equation}
In this more general case, we have again that the disease cannot spread when $\theta \geq \RR$.

@@

Like $g$, $b$ is a distribution: in this case the initial backward generation interval, which gives the distribution of realized generation times when the disease spreads exponentially \cite{Champ}.

Now imagine an intervention that reduces transmission at a constant hazard rate $h$ across the disease generation, for example by identifying and isolating infectious individuals.
We then have:
\begin{equation}
	\hat K(\tau) = K(\tau)\exp(-h\tau) = b(\tau)\exp((r-h)\tau)
\end{equation}
Since $b$ is a distribution, the reduction needed to prevent invasion (or to eliminate disease)  is exactly $h=r$. We call $h$ the ``speed'' of the intervention; transmission is interrupted when the speed of the intervention is larger than the speed of spread.

We define the strength of a general intervention $L(\tau)$ \eqref{Ldef} to be $\phi = r - \hat r$. We can then show that $\phi$ is a (sort of) mean satisfying:
\begin{equation}
	1 = \left\langle \frac{\exp(\phi \tau) }{L(\tau)} \right\rangle_{b(\tau)}
\end{equation}
